\huge Fast Evaluation of Intermolecular Charge Transfer Energy: New Approach Based on One-Electron Effective Potentials

### 2019-06-29 papers/conference/1.MQM_2019/poster-84x118cm.tex
Some revision

\begin{textblock*}{250mm}(10mm,261mm)
\begin{block}{Our Approach}
 \begin{itemize}
   \item Consider Murrell et al.'s perturbation theory [5]
   \item Apply OEP method to eliminate ERI's
   \item Adapt the CT term to the EFP2 method [2,3]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{180mm}(270mm,261mm)
\begin{block}{CT energy by Murrell et al. [5]}
  \vskip-2ex
  \begin{equation*}
    \Delta E_{\rm CT}^{A\rightarrow B} = 2\sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir}
     \frac{\vert V_{in}^{A\rightarrow B} \vert^2 }{\varepsilon_i - \varepsilon_n}
  \end{equation*}
  \vskip0.4ex
\end{block}
\end{textblock*}

@@

\begin{textblock*}{367mm}(463mm,233mm)
\begin{exampleblock}{Types of matrix elements of OEP operators}
\vskip0.1ex
\begin{table}[b]
\def\arraystretch{1.2}
\begin{tabular}{lcccc}
Matrix element      &&            `Overlap-like'                &&            `Coulomb-like'               \\ 
                    && $\tBraKet{i}{\hat{v}_{\rm eff}^{A}}{j} $ && $\tBraKet{j}{\hat{v}_{\rm eff}^{A}}{l}$ \\ 
	\cline{1-5}
Partitioning scheme &&            $i\in A, j\in B$              &&               $j,l\in B$                \\
Associated ERI's    &&            $\BraKet{AA}{AB}$             &&               $\BraKet{AA}{BB}$         \\
Handling            && Density Fitting                          && Distributed Multipoles                  \\
\end{tabular}
%
\end{table}
\vskip-0.1ex
\end{exampleblock}
\end{textblock*}

@@

% - Scheme 
\begin{textblock*}{820mm}(10mm,355mm)
\begin{exampleblock}{Coupling Constant $\boldsymbol{ V_{in}^{A\rightarrow B} } $}
\begin{figure}
\includegraphics[width=1.0\textwidth]{scheme-r1.eps}
\vskip0.9ex
\caption{\bf Application of the OEP technique to significantly simplify original theory of Murrell et al. [5] 
             EFP parameters are shown in blue.}
\end{figure}
\end{exampleblock}
\end{textblock*}

@@

\begin{textblock*}{257mm}(573mm,824mm)
\begin{block}{Summary and Outlook}
 \begin{itemize}
   \item OEP-based model reproduces CT energies of the parent Murrell et al.'s [5] model
   \item OEP-based model is 4-7 times faster than EFP2
   \item Further optimization is possible: using QUAMBO orbitals [4]
   \item OEP's can be applied to other problems as well
 \end{itemize}
\end{block}
\end{textblock*}

>>>>

\begin{textblock*}{249mm}(10mm,261mm)
\begin{block}{Our Approach}
 \begin{itemize}
   \item Consider Murrell et al.'s perturbation theory [5]
   \item Apply OEP method to eliminate ERI's
   \item Adapt the CT term to the EFP2 method [2,3]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{180mm}(270mm,261mm)
\begin{block}{CT Energy by Murrell et al. [5]}
  \vskip-2ex
  \begin{equation*}
    \Delta E_{\rm CT}^{A\rightarrow B} = 2\sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir}
     \frac{\vert V_{in}^{A\rightarrow B} \vert^2 }{\varepsilon_i - \varepsilon_n}
  \end{equation*}
  \vskip0.4ex
\end{block}
\end{textblock*}

@@

\begin{textblock*}{367mm}(463mm,233mm)
\begin{exampleblock}{Types of Matrix Elements of OEP Operators}
\vskip0.1ex
\begin{table}[b]
\def\arraystretch{1.2}
\begin{tabular}{lcccc}
Matrix element      &&            `Overlap-like'                &&            `Coulomb-like'               \\ 
                    && $\tBraKet{i}{\hat{v}_{\rm eff}^{A}}{j} $ && $\tBraKet{j}{\hat{v}_{\rm eff}^{A}}{l}$ \\ 
	\cline{1-5}
Partitioning scheme &&            $i\in A, j\in B$              &&               $j,l\in B$                \\
Associated ERI's    &&            $\BraKet{AA}{AB}$             &&               $\BraKet{AA}{BB}$         \\
Handling            && Density Fitting                          && Distributed Multipoles                  \\
\end{tabular}
%
\end{table}
\vskip-0.1ex
\end{exampleblock}
\end{textblock*}

@@

% - Scheme 
\begin{textblock*}{820mm}(10mm,355mm)
\begin{exampleblock}{Coupling Constant $\boldsymbol{ V_{in}^{A\rightarrow B} } $}
\begin{figure}
\includegraphics[width=1.0\textwidth]{scheme-r1.eps}
\vskip0.9ex
\caption{\bf Application of the OEP technique to significantly simplify original theory of Murrell et al. [5] (left). 
             Fragment parameters are shown in blue.}
\end{figure}
\end{exampleblock}
\end{textblock*}

@@

\begin{textblock*}{257mm}(573mm,824mm)
\begin{block}{Summary and Outlook}
 \begin{itemize}
   \item OEP-based model {\color{blue} reproduces} CT energies of the parent Murrell et al.'s [5] model
   \item OEP-based model is 4-7 times {\color{blue} faster} than EFP2
   \item Further optimization is {\color{blue} possible}: using QUAMBO orbitals [4]
   \item OEP's can be applied to {\color{blue} other problems} as well
 \end{itemize}
\end{block}
\end{textblock*}
